### 2016-09-28 intro.tex
comments in intro

\heading{Comparison to~\cite{naor2015bloom}.} Naor and
Yogev~\cite{naor2015bloom} recently considered the problem of
adversarial soundness for (variants of) Bloom filters and, indeed,
their worked served as inspiration for our own. Our work extends
their work significantly in several directions. For starters, we
consider abstract data structures (rather than only the case of
set-membership data structures), and consider privacy in addition to
soundness. Even with respect to the specific case of soundness for
set-membership data structures, our work offers several advantages
to the Naor-Yogev treatment:
\begin{itemize}
\item We explicitly distinguish between public and private
    portions of a data structure, something that was left
    ambiguous in~\cite{naor2015bloom}. This allows us, for
    example, to distinguish between the hash-function keys and
    the bit array when discussing classical Bloom filters.
\item The Naor-Yogev definition of soundness allows the
    adversary to make several set-membership queries, some of
    which may produce incorrect results, and the attacker then
    succeeds if it can output a \emph{fresh} query which leads
    to an error. We propose instead what we find to be a more
    natural definition in which the attacker succeeds if it can
    cause a certain number of incorrect results.
\item Naor and Yogev analyze a new Bloom-filter construction of
    their own design. In contrast, we are interested in
    analyzing practical constructions that have been proposed in
    prior work to understand how secure they are. In particular,
    we analyze Bloom filters in the random-oracle model.
    \jnote{Do we? Perhaps we want to explicitly adapt some of
    our definitions to the ROM?}
\end{itemize}

%false-positive error, is a parameter of the Bloom filter.  (The
%values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
%well-known way.) NY recast this soundness condition as a game in
%which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
%set-membership queries, and it attempts to find one or more false
%positives. The fact that~$A$ can \emph{adapt} its queries and its
%output based on what it learns from the set-membership oracle (but,
%as we will see, not upon the hash functions) is the key definitional
%contribution of~NY.

>>>>

\heading{Comparison to~\cite{naor2015bloom}.} Naor and
Yogev~\cite{naor2015bloom} recently considered the problem of
adversarial soundness for Bloom filters and, indeed,
their worked served as inspiration for our own. Our work extends
their work significantly in several directions. For starters, we
consider abstract data structures (rather than only the case of
set-membership data structures), and consider privacy in addition to
soundness. Even with respect to the specific case of soundness for
set-membership data structures, our work offers several advantages
to the Naor-Yogev treatment:
\begin{itemize}
\item We explicitly distinguish between public and private
    portions of a data structure, something that was left
    ambiguous in~\cite{naor2015bloom}. This allows us, for
    example, to distinguish between the hash-function keys and
    the bit array when discussing classical Bloom filters.
\item The Naor-Yogev definition of soundness allows the
    adversary to make several set-membership queries, some of
    which may produce incorrect results, and the attacker then
    succeeds if it can output a \emph{fresh} query which leads
    to an error. We propose instead what we find to be a more
    natural definition in which the attacker succeeds if it can
    cause a certain number of incorrect results.
\item Naor and Yogev analyze a new Bloom-filter construction of
    their own design. In contrast, we are interested in
    analyzing practical constructions that have been proposed in
    prior work to understand how secure they are. In particular,
    we analyze Bloom filters in the random-oracle model.
    \jnote{Do we? Perhaps we want to explicitly adapt some of
    our definitions to the ROM?}
\end{itemize}
\tsnote{I think we can say a bit more here about what they show, and
  why their presentation is lacking, certainly as a work that anchors
  an important area of study.  This feels a bit weak, at the moment.
  For example, at the opening of this section we say they consider
  ``adversarial soundness for Bloom filters'', but I assert that it
  isn't clear that their syntax allows them to study Bloom filters at all.}
We give a more detailed comparison to, and criticism of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}.

\todo{Describe the BF variants we consider, and briefly why they are
  natural/interesting.}
\todo{Surface contribution of setting the stage for a bunch of future
  work: dynamic data-structures (including counting BFs, stable BFs,
  hierachical BFs, count-min-sketches, etc.); security of common
  usages of BF and related data structrues (e.g. CDNs and other
  distributed storage, find more); more generally bringing to the
  attention of the community the need to give proper cryptographic
  treatment to data structures (which may not have been conceived with
  security-critical applications in mind but have been co-opted for
  them (like BFs).}
%false-positive error, is a parameter of the Bloom filter.  (The
%values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
%well-known way.) NY recast this soundness condition as a game in
%which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
%set-membership queries, and it attempts to find one or more false
%positives. The fact that~$A$ can \emph{adapt} its queries and its
%output based on what it learns from the set-membership oracle (but,
%as we will see, not upon the hash functions) is the key definitional
%contribution of~NY.
